Human tissue specific markers

### 2017-06-08 manuscript/manuscript.Rnw
add discussion of parts of paper

@@

@@

\Sexpr{star.logs[grepl("Number of input reads",field),sum(as.numeric(value))]} %
%
RNAseq reads from %
%
\Sexpr{length(star.logs[grepl("Number of input reads",field),value])} %
% 
samples (supplemented with FPKMs from
\Sexpr{nrow(predictions.caret.svm[["uterus"]][["training"]])+
  nrow(predictions.caret.svm[["uterus"]][["testing"]]) -
  length(star.logs[grepl("Number of input reads",field),value])} %
%
additional samples without raw data in the \ac{SRA}) corresponding
to %
\Sexpr{length(unique(na.omit(tissue.specific.genes[,tissue])))} %
different tissues were obtained from the Roadmap Epigenomics
\cite{Bernstein.ea2010:NIHRoadmapEpigenomicsMapping} and GTEx
\cite{Gtexconsortium.2015:Thegenotypetissueexpression} projects, as
well as uterine (GSE50599,
\cite{Chan.ea2014:Assessmentofmyometrialtranscriptome}) and placenta
(GSE66622, \cite{Hughes.ea2015:Evaluatingintra-andinter-individual})
samples from the \ac{SRA}.

Reads were aligned to \textit{Homo sapiens} reference genome GRCh38
with Ensembl annotation release 80 using STAR v2.4.2a
\cite{Dobin.ea2013:STARultrafastuniversalRNA-seq} and called using
Cufflinks v2.2.1
\cite{Trapnell.ea2009:TopHatdiscoveringsplicejunctions}. The average
percentage of uniquely mapped reads was %
\Sexpr{mean(as.numeric(gsub("%","",star.logs[field=="Uniquely mapped reads %",value])))}\%
and the average total mapping percentage was %
\Sexpr{mean(as.numeric(gsub("%","",star.logs[field=="Uniquely mapped reads %",value]))+as.numeric(gsub("%","",star.logs[field=="% of reads mapped to multiple loci",value])))}\%.
% 
For samples where the reads were not publicly available (GTEx and
some Roadmap Epigenomics samples), the RPKM were taken from publicly
available result files (see code for details).

\subsection{Tissue Specificity}

>>>>

In this paper we want to show that given a population of \ac{EV}

\textbf{Can we determine the proportions and identities of
  the tissue(s) of \ac{EV} origin?}

\textbf{Can assign differential expression to a particular tissue of
  origin in \ac{EV}?}

\textbf{Housekeeping genes are not tissue specific}

\textbf{Additional genes which are likely to be housekeeping but were
  not identified by previous papers}

@@

\subsection{\ac{EV} background}

\paragraph{What are \acsp{EV}}

\paragraph{Where are \acsp{EV} found?}

\paragraph{How are \acsp{EV} formed and what are their contents}

\subsection{\acsp{EV} will enable routine liquid biopsies}

\paragraph{Existing work showing promise of \acsp{EV}}

\paragraph{Existing methods require tumor/disease specific marker which is unique to that tissue}

\subsection{Identifying tissues of origin}

\paragraph{Existing protein surface markers}

\DLA{Is there a database of tissue/cell specific markers?}

\paragraph{Issues of single cell transcriptome heterogeneity}

\paragraph{Tissue specificity index}

\subsection{Assigning differential expression}

@@

\subsubsection{Samples}
\Sexpr{star.logs[grepl("Number of input reads",field),sum(as.numeric(value))]} %
%
RNAseq reads from %
%
\Sexpr{length(star.logs[grepl("Number of input reads",field),value])} %
% 
samples (supplemented with FPKMs from
\Sexpr{nrow(predictions.caret.svm[["uterus"]][["training"]])+
  nrow(predictions.caret.svm[["uterus"]][["testing"]]) -
  length(star.logs[grepl("Number of input reads",field),value])} %
%
additional samples without raw data in the \ac{SRA}) corresponding
to %
\Sexpr{length(unique(na.omit(tissue.specific.genes[,tissue])))} %
different tissues were obtained from the Roadmap Epigenomics
\cite{Bernstein.ea2010:NIHRoadmapEpigenomicsMapping} and GTEx
\cite{Gtexconsortium.2015:Thegenotypetissueexpression} projects, as
well as uterine (GSE50599,
\cite{Chan.ea2014:Assessmentofmyometrialtranscriptome}) and placenta
(GSE66622, \cite{Hughes.ea2015:Evaluatingintra-andinter-individual})
samples from the \ac{SRA}.

\subsubsection{Alignment and Calling}
Reads were aligned to \textit{Homo sapiens} reference genome GRCh38
with Ensembl annotation release 80 using STAR v2.4.2a
\cite{Dobin.ea2013:STARultrafastuniversalRNA-seq} and called using
Cufflinks v2.2.1
\cite{Trapnell.ea2009:TopHatdiscoveringsplicejunctions}. The average
percentage of uniquely mapped reads was %
\Sexpr{mean(as.numeric(gsub("%","",star.logs[field=="Uniquely mapped reads %",value])))}\%
and the average total mapping percentage was %
\Sexpr{mean(as.numeric(gsub("%","",star.logs[field=="Uniquely mapped reads %",value]))+as.numeric(gsub("%","",star.logs[field=="% of reads mapped to multiple loci",value])))}\%.
% 
For samples where the reads were not publicly available (GTEx and
some Roadmap Epigenomics samples), the RPKM were taken from publicly
available result files (see code for details).

\subsubsection{Normalization}

\subsection{Tissue Specific Markers}

\subsubsection{Tissue Specificity Index}
